\Huge \bf \sc Calibration of an inertial measurement unit

### 2013-07-29 latex/paper_sensores/paper.tex
mas

\begin{abstract}
%\boldmath
This paper presents a way to calibrate different inertial measurement sensors. In particular we present the calibration of an accelerometer and a gyroscope using least square. A model of the sensors is presented based on the main errors that MEMS devices present, a calibration method is proposed for the static parameters of the model. Finally a temperature adjust is made.  
% -cambio-
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

\section{Introduction}
The development of the Micro-electromechanical Systems(MEMS) technology has allowed to manufacture many low-cost chip-sensors, such as accelerometers, gyroscopes and magnetometers. Those chips have been adopted in many applications, for instance Inertial Navigation Systems (INS)\cite{bib:paper}. However this sensors have many error sources, thus they must be calibrated before being used and they should be re-calibrated periodically for any precision application. The different sources of error will be analysed in more detail in section \refp{sec:modelo} and the implications of those errors will be derived.\\

>>>>

\begin{abstract}
%\boldmath
This paper presents a way to calibrate different inertial measurement sensors. In particular we present the calibration of an accelerometer and a gyroscope using nonlinear least squares. A model of the sensors is presented based on the main errors that MEMS devices present, a calibration method is proposed for the static parameters of the model. Finally a temperature adjust is made.  
% -cambio-
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

\section{Introduction}
The development of the Micro-electromechanical Systems (MEMS) technology has allowed to manufacture many low-cost chip-sensors, such as accelerometers, gyroscopes and magnetometers. Those chips have been adopted in many applications, for instance Inertial Navigation Systems  (INS)\cite{bib:un_puto_nuevo}. However this sensors have many error sources, thus they must be calibrated before being used and they should be re-calibrated periodically for any precision application. The different sources of error will be analysed in more detail in section \refp{sec:modelo} and the implications of those errors will be derived.\\
